Radiance - A Web Application Environment

### 2016-12-19 els2017-radiance/paper.tex
Attempt to rewrite the introduction to be less shit.

%% FIXME:
% As it stands the paper's introduction is garbage.
% Either:
%   Show examples for shitty frameworks that can't do what Radiance can
%   Focus more on the new perspective rather than making the impossible possible

@@

\keywords{Common Lisp, web framework, web development, encapsulation, interfacing}

\section{Introduction}
Most tasks involved in writing a website or web application are not very complex or complicated; they usually involve performing very similar tasks every time. This trend lead to the rise of web frameworks-- collections of tools and libraries to take care of the most common of aspects for the developer. \\

A web application framework is comprised of several components. This can go from the absolute minimum of an HTTP server and URL dispatch mechanism as seen in microframeworks\cite{microframeworks}, to a vast range of tools including database access, authentication, user management, validation, API endpoints, and more. All of the components exist with the aim of reducing the amount of work necessary to write a single web application. \\

Often these frameworks do not address many questions about deployment and server setup. The assumption is made that the application will be deployed in such a fashion that it is run on a single public-facing domain, which it has complete control over. More specifically, it is assumed that the full path of the URL can be controlled. This assumption leads to complications when multiple applications should be run on the same server. Sharing can be accomplished by using different ports for each application's server, and then using a proxying server that defers requests to the appropriate application depending on the subdomain of the request. \\

However, this does not account for all possible setups. For example, if one cannot add subdomains and would prefer to run the applications under different path prefixes, it will frequently not be possible to run the application properly. While URL rewriting by the proxying server can be used to at least get the application to dispatch, the HTTP documents returned by it will contain links that are not properly resolved and will point to invalid resources. \\

This problem leads to a divide in application design. If the task is to write an application that others should be able to use on their own setup, then it needs to be written in a particular way in order to account for the aforementioned setup differences. The framework will usually not help with this in any way, and an ad-hoc solution has to be written. As an example, Wordpress requires the configuration of a special variable to account for this.\cite{wordpress} \\

For administrators the problems that stem from these single-application focused frameworks do not end there, however. Many applications will need access to the same kinds of resources. Frequently, information about users, authorisation, sessions, and so forth should be shared, but cannot, because the various applications were designed individually, without any concern for standardised access of such resources. As such, running multiple applications on the same server results in duplication of information. This duplication can be especially cumbersome for the users, as they need to track multiple registrations, profiles, and so forth, despite being on the same service. \\

>>>>

@@

\keywords{Common Lisp, web framework, web development, encapsulation, interfacing}
\newpage

\section{Introduction}
Most tasks involved in writing a website or web application are not very complex or complicated; they usually involve solving very similar problems every time. This trend lead to the rise of web frameworks-- collections of tools and libraries to take care of the most common of aspects for the developer. \\

A web application framework is comprised of several components. This can go from the absolute minimum of an HTTP server and URL dispatch mechanism as seen in microframeworks\cite{microframeworks}, to a vast range of tools including database access, authentication, user management, validation, API endpoints, and more. All of these components exist with the aim of reducing the amount of work necessary to write a single web application. \\

Usually these frameworks have the goal of supporting developers in writing a single, particular application. This can lead to issues when the application is supposed to be deployed on wildly different setups than it was developed on, or if it should share the space with other applications. Solutions to resource sharing or configuration then have to be designed by the application itself, and are thus often ad-hoc and incompatible with other applications. As an example, even if you have two applications like a forum and a blog that were both written with the same framework, you won't feasibly be able to configure your system in such a way that both share the same login and account information. \\

This leads to a frustrating experience for the administrator of a server setup, who either has to go through complicated deployment and configuration steps to bend the applications to fit his requirements, or even has to go so far as to change the source code to do what he needs.
